\documentclass{article}
\usepackage[utf8]{inputenc}

\title{cse13s essay}
\author{Isabella Phung}
\date{January 2023}

\begin{document}

\maketitle

\section{Introduction}
Eco's point is true in my opinion. Modern day society is heavily reliant on the internet for information. There is constantly new media, new shows, new things to talk about. it seems like theres an event everyday and huge stories seem like old news after three days. There are many different factors that contribute to this phenomenon but Twitter has been an especially prominent example as of late with Musk's 300 billion dollar purchase of the company. For many, twitter is their main form of entertainment, communication, and news source. with the brevity of posts, it's difficult to make serious, concrete arguments or announcements citing specific sources. The format of replying, quote replying, private retweeting, all of these different ways of adapting someone else's words onto your own page, well, you're not required to respond, or respond well. There's a culture of unintelectualism that has brewed for years. Tiktok, tumblr, twitter, are all prime examples, where anyone can make a post that spins up a tale or a "fact" for views, and people will immediately agree without taking the time to search for other sources, to question. this encourages influencers to post and talk about what's popular or what the audience wahts to talk about rather than what the audience should know about. this has persisted in other forms of media beyond internet social media, but it's on a very large scale that is influencing a generation of children to believe in what's easy rather than the truth.
there are other deep social factors that also contribute (non-standardized education making it difficult to push for critical reading skills across America and the world, socio-economic factors that make spending the time to search through info and inform oneself to be difficult for people of middle to low class.) there's this pressure to be informed and caught up and to know everything. you haven't caught up with this show? another thing to watch. How come there isn't more attention on this? if you scroll past, you're a terrible person. That's not to say it's bad to be informed, but it's suffocating for the average person. There's also a dopamine rush that comes with using the internet, when seeing something funny, when communicating and connecting with others. Eco does describe noise as a form of censorship but he does not necessarily distinguish real important news as not noise either. What's considered crucial will depend on the audience of course. but in many ways real news can contribute to the noise. much in the same way Eco uses the example of planting a bomb in order to hides ones crimes in the newspaper, the oversatuation of news creates noise. It's hard to sift and parse through stories to find what really matters when it seems like everything matters. But it's unrealistic to expect one person to be constantly up to date with the politics and nuance of every country on earth; even the big players. Even if media takes the time to go as in depth as possible into a story, they can't spend the air time to give a history lesson on each country. Huge events are often interconnected in ways that news just can't extrapolate upon.
Eco's conclusion focuses on the concept of silence. He admittedly not so much as explores it as he does simply provoke the reader to investigate it themselves, but he brings up a flurry of diferent situations and prompts in regards to what silence means in our culture and society. The first thoughts that come to mind with silence is inaction. But in a world where noise is easy to produce and so readily abundant, silence speaks volumes. Silence makes for an especially difficult medium to utilize as it's so highly context driven. Some might describe it as reading between the lines; what's written is important but just as much as what is \textit{not} written. Silence can be used in serious situations, it can indicate disapproval, when glaring at someone. It can mean quiet anger as someone steeps in their rage. It can mean surprise while someone is stunned to silence. It can be used with positive conotations as well. Silence is key in humor and delivering jokes. A silent audience can be one that's unentertained, but also one so enraptured, they hesitate to make a sound.  
A particularly tricky subject that Eco brings up is the ways that media influences people as it reports various crimes and subjects. Eco describes, "the press generates revenge attacks, suicides, classroom shootings-- news about one school shooting provokes other school shootings, and a great many Romanians have probably been encouraged to rape old ladies because the newspapers told them it is the exclusive speciality of immigrants and is extremely easy to commit." Whether or not this is true is difficult to say. There are some philisophical elements regarding humans and if humanity is innately evil. One of his examples, school shootings have been prevalent in America, but is extremely uncommon in Europe despite the news still covering school shootings. News does greatly influence its audience, that is true, but there are certainly outside factors contributing to crime. Placing the blame on media and news solely can lead down a slippery slope of denying the truth of news. It's also true that media is super saturated with negative events rather than celabrating the joys and triumphs of life and humanity. There has to be a balance between consuming mediato stay informed on current events and being able to take a step back and reflect on the information being absorbed. In being able to reflect on what we read or watch, we can better sift through the noise. 
\end{document}
